Long-range correlations in high-multiplicity proton--proton collisions at \s~=~\unit[13]{TeV} with ALICE at the LHC

### 2019-11-19 paper.tex
updates

Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions. Recent center-of-mass energy of colliding two protons is increased up to \unit[13]{TeV} during LHC Run2 period. Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2017 data sets.

The full description of ALICE detector in the LHC Run 2 can be found in Ref. \cite{ALICEdet}. The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors. The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively. The V0 provides trigger and estimation of event multiplicity. A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector. The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD). ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction. The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC. The tracking of charged-particles is done with the combination of ITS and TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.

Subsystems mainly used in the present analysis, VZERO detector, Inner Tracking System(ITS) and Time Projection Chamber(TPC), are mainly discussed in the paper while the whole ALICE detector is well described in Ref. \cite{ALICEdet}. The VZERO is separated into two plates, VZERO-A and VZERO-C, consisting of two arrays of 32 scintillator tiles each, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively. The VZERO provides trigger and event characterization with respect to particle abundance. With higher threshold, High Multiplicity Trigger can be implemented by VZERO to acquire very high multiplicity events exclusively.

The responsibility of reconstruction of charged track is up to the ITS and the TPC. The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon DriftDetector (SDD) and Silicon Strip Detector(SSD). ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction. The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC. The tracking of charged-particles is done with the combination of ITS and TPC, which also enable to reconstruct low transverse momentum tracks down to 0.15 GeV/\it{c}\rm{} with $\sim$70\% efficiency.

>>>>

Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions. Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period. Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.

The full description of ALICE detector in the LHC Run 2 can be found in Ref. \cite{ALICEdet}. The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors. The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively. The V0 provides trigger and estimation of event multiplicity. A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector.

The responsibility of reconstruction of charged track is up to the ITS and the TPC. The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD). The ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction. The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC. The tracking of charged-particles is done with the combination of the ITS and the TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
